Paper notes

### 2019-08-22 paper_notes.Rmd
Add files via upload

# ethnic utility difference and value utility difference

@@

dfprob
# Probability to move to alternative (random utility with logistic regression)

@@

@@

@@

@@

```{r logistic, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}

magic_for()

e_w <- 0.5
v_w <- 0.5
k <- 10

for (d_u_e in seq (-1.0,1.0, by = 0.1)){

dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w,k)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w,k)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w,k)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w,k)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w,k)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w,k)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w,k)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w,k)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w,k)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w,k)
dis_0   <- prob(d_u_e,0.0,e_w,v_w,k)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w,k)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w,k)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w,k)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w,k)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w,k)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w,k)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w,k)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w,k)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w,k)
dis_1   <- prob(d_u_e,1.0,e_w,v_w,k)

  value_difference <- seq(-1.0,1.0, by = 0.1)

@@

  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",d_u_e)
  title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10
                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
                           )

@@

 final_prob <-  suppressWarnings(suppressMessages(
    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
      labs(title=title_cond_prob, caption = title_caption)

      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted") 
  ))

@@

```{r test, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}

e_w_v <- 0.5
v_w_v <- 1-e_w_v
k_v <- 10

dfprob_log <- mutate(dfprob,e_w=e_w_v,v_w=v_w_v,k=k_v, probalog = prob(d_u_e, d_u_v,e_w,v_w,k))

#  report_prob <- na.omit(dfprob_log(d_u_v,probalog))

logi <- function(lo){
plot_report_prob <- ggplot(dfprob_log[which(d_u_e == lo),],aes(d_u_v,probalog))

  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",lo)
  title_caption <-  paste0("Ethnic weight = ",e_w_v*k_v," ; ","Value weight = ",v_w_v*k_v
                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
                           )

 final_prob <-  suppressWarnings(suppressMessages(
    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
      labs(title=title_cond_prob, caption = title_caption)

      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
  ))

 final_prob

logi(-1)
logi(-0.9)

>>>>

# Ethnic utility difference and value utility difference

@@

# Probability to move to alternative (random utility with logistic regression)

@@

# For the 3D plots

@@

# ANNEX {-}

## Ethnic Utility Calculation

@@

## Value Utility Calculation {-}

@@

## Logistic Function calculation {-}

```{r logistic, fig.width=5,fig.height=3,fig.align='left',include=TRUE, echo=FALSE}

# PROBABILITY to relocate to alternative
# Choose the parameters for ethnic weight (e_w), value weight (v_w) and the cstant k. As default v_w is complementar to e_w (1-e_w, as will be in the abm), you can change this.
# The parameter for importance of relative utility is equal to e_w*k for ethnic utility and v_w*k for value utility. The highest the parameter for that dimension, the less random is the choice and the more depending on the option with highest relative utility
# Each vignette is one level of ethnic utility difference (-1 to 1), the x-axis the value-difference (-1 to 1), on y-axis the probability to relocate.

e_w <- 0.5              
v_w <- 1-e_w
k <- 10

for (d_u_e in seq (-1.0,1.0, by = 0.1)){    # Runs the same function for each level of ethnic utility difference
                                            # d_u_e, the increasing number is the value utility difference
dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w,k)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w,k)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w,k)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w,k)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w,k)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w,k)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w,k)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w,k)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w,k)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w,k)
dis_0   <- prob(d_u_e,0.0,e_w,v_w,k)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w,k)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w,k)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w,k)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w,k)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w,k)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w,k)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w,k)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w,k)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w,k)
dis_1   <- prob(d_u_e,1.0,e_w,v_w,k)

value_difference <- seq(-1.0,1.0, by = 0.1)       # here to setup the plot and change info for each vignette

@@

title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",d_u_e)
title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative")

@@

final_prob <-  suppressWarnings(suppressMessages(plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") + labs(title=title_cond_prob, caption = title_caption) + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")))

@@
